%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[colorlinks, urlcolor=black]{hyperref}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\simpleItem}[1]{
  \item\small{
    { #1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\linespread{1.6}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Huge Yunxin Sun} & Email : {martin.yunxin.sun@gmail.com}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education Background}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tongji University}{Sep \,2016 -- Jul \,2020 (expected)}
      {B.S. in Software Engineering(Digital Media Technology)}{GPA:\,90.68/100 \quad Ranking:\,Top 5\%}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Research Experiences}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Pulmonary Nodule Malignancy Classification with CNN}{Tongji University, Shanghai}
      {Research Assistant}{Sep 2017 - Jan 2018}
      \resumeItemListStart
        \simpleItem
          {Proposed a novel 3D CNN architecture with the help of Dr.Guokai Zhang.}
        \simpleItem
          {Gained hands-on experience with PyTorch and network training.}
      \resumeItemListEnd

      \resumeSubheading
        {Sketch-based 3D model Retrieval}{Tongji University, Shanghai}
        {Research Assistant}{Feb 2018 - May 2018}
        \resumeItemListStart
          \simpleItem
            {Systematically surveyed literatures regarding image retrieval and sketch recognition.}
          \simpleItem
            {Learned sketch-related computer graphics algorithms myself.}
        \resumeItemListEnd

      \resumeSubheading
        {Intelligent User Interfaces for Visualization}{Tongji University, Shanghai}
        {Research Assistant}{Jun 2018 - present}
        \resumeItemListStart
          \simpleItem
            {Built an interactive web system with modern front-end frameworks to collect user behaviour data.}
          \simpleItem{Learned Recommendation}
        \resumeItemListEnd



  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Awards}
  \resumeSubHeadingListStart
    \item Scholarship for Excellent Academic Performance \hfill {2017, 2018}
    %\resumeSubItem{QuantSoftware Toolkit}
    %  {Open source python library for financial data analysis and machine learning for finance.}
    %\resumeSubItem{Github Visualization}
    %  {Data Visualization of Git Log data using D3 to analyze project trends over time.}
    %\resumeSubItem{Recommendation System}
    %  {Music and Movie recommender systems using collaborative filtering on public datasets.}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \resumeSubItem{Programming Languages}
   {Python, JavaScript, C/C++, Matlab, C$^{\#}$, Assembly Language.}
   \resumeSubItem{Tools \& Software}
   {Git, Linux, \LaTeX , Arduino, Raspberry Pi, Unity, Maya.}
   \resumeSubItem{Frameworks}
   {Node, React Native, Ruff, Vue, D3, PyTorch, scikit-learn, Pandas, Numpy.}

 \resumeSubHeadingListEnd

\section{Publications}
\resumeSubHeadingListStart
\item G.K.Zhang, Y.Luo, D.D.Zhu, Y.X.Xu, \textbf{Y.X.Sun}, J.W.Lu.(2018). Spatial Pyramid Dilated Network for Pulmonary Nodule Malignancy Classification. In \emph{Proceedings of International Conference on Pattern Recognition(ICPR'18).}(Accepted).
\resumeSubHeadingListEnd
%-------------------------------------------
\section{Core Courses}
\resumeSubHeadingListStart
\resumeSubItem{\small{CS}}
{{User Interface Technologies, Computer Vision, Computer Networks, Algorithms, Data Structures, Operating Systems, Compilers, Computer Architecture, Computer Graphics(ongoing), Digital Image Processing(ongoing).}}
\resumeSubItem{Math}
{Calculus, Linear Algebra, Probability and Statistics, Numerical Analysis,Complex Analysis, Discrete Mathematics, Combinatorics}
\resumeSubItem{Data Science}
{\href {https://www.coursera.org/account/accomplishments/verify/LWTSBR9KPCBS}{{Data Mining(online)}}, \href{https://www.coursera.org/account/accomplishments/verify/PUK2K8PA69QF
}{{Machine Learning(online)}}, \href{https://www.coursera.org/account/accomplishments/specialization/QF7KAZ8WKEB2}{{Deep Learning(online)}}, \href{https://www.coursera.org/account/accomplishments/verify/YW47GT8YU4G8}{{Data Manipulation at Scale(online)}}.}
\resumeSubItem{Engineering}
{Theoretical Mechanics, Mechanics of Materials, Circuit Theory, Analog Electronics, Creative Product Development, Engineering Practice.}

\resumeSubHeadingListEnd
\end{document}
